The fundamental pillars of Rscience are __*Reproducibility*__, __*Transparency*__, and __*Open Access*__.  
We strongly believe that adherence to these principles helps make science better, more reliable, and more objective.

This section provides a complete digital footprint of the computational environment used to generate this report.

By documenting the exact R version, Rscience version, the operating system configuration, and the precise list of installed packages, we guarantee maximum transparency and portability of the analysis, ensuring that the results presented can be accurately validated and replicated by any third party.

To achieve true, byte-for-byte reproducibility, a set of explicit commands leveraging the rix library is provided. These statements enable users to install the exact version of R and Rscience used when generating this report, along with every required dependency package locked to its specific version. This process eliminates environmental variance and ensures the analysis can be faithfully recreated across different systems.

### R - Session Info
Shows the currently loaded packages and R environment configuration for this specific analysis. This includes R version, locale settings, and attached packages that are actively being used in this report.

```{r}
sessionInfo()
```




### R Version
```{r include=TRUE, eval=FALSE, echo = TRUE}
R.version
```
```{r include=TRUE, eval=TRUE, echo = FALSE}
df_libraries <- as.data.frame(unlist(R.version))
df_libraries <- cbind.data.frame(rownames(df_libraries), df_libraries)
colnames(df_libraries) <- c("Parameters", "values")
rownames(df_libraries) <- NULL
kable(df_libraries, align = "ll", format = "html")
```




### R - Installed Libraries
Lists all packages installed in the R environment, providing a complete inventory of available tools. This comprehensive list helps recreate the computational environment for reproducibility purposes.

```{r, eval=FALSE, echo=TRUE}
installed.packages()
```
```{r installed-libraries, include=TRUE, eval=TRUE, echo=FALSE}
# El código para mostrar el comando DEBE ir en el mismo chunk que genera la tabla
#installed.packages()

# R - System Info
df_installed_libreries <- installed.packages()

DT::datatable(
  df_installed_libreries,
  options = list(
    pageLength = 10, # Sets the default number of rows per page to 10
    lengthMenu = c(5, 10, 25, 50) # Provides options to change rows per page
  )
)
```
