---
title: "Rscience"
format: docx
---

```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}

 #Cargar configuración desde _quarto.yml
library(yaml)
config <- yaml::read_yaml("_quarto.yml")

# Folders
str_output_folder <- config$my_global_folders$USER_OUTPUT_FOLDER
str_png_folder <- config$my_global_folders$png_folder

# Input paths
str_input_file_path_RData        <- config$list_input_file_path$str_file_path_RData

# Output file names


# Extra output file
str_output_file_name_report_docx <- c(config$format$docx$"output-file")


# Loading objects
load(str_input_file_path_RData)

```


# Section 01 - Libraries
Lo primero que haremos siempre será cargar las librerias necesarias para obtener 
la totalidad de las tablas, gráficos y test estadísticos.
```{r eval=TRUE, echo=TRUE, message=FALSE, warning=FALSE}
# # # # # Section 01 - Libraries ---------------------------------------------
  library("stats")     # General Linear Models
  library("agricolae") # Tukey test
  library("plotly")    # Advanced graphical functions
  library("dplyr")     # Developing with %>%
  library("stringr")   # Strings replacement
  library("EnvStats")  # QQplot

source("fns.R")

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 6,
  fig.height = 4,
  dpi = 150,
  fig.align = "center"
)

```




\newpage
# Anova Outpus
## Anova Table
```{r include=TRUE}
fn_show_table_dynamic(object_name = "df_table_anova_classroom", caption_text = "")

```

## Tukey Table and Plot
```{r include=TRUE}
fn_show_table_dynamic(object_name = "df_tukey_table_classroom", caption_text = "")

```

```{r}
#| warning: false
#| echo: false
plot007_factor
```

## Requeriments - Residuals Normality
```{r include=TRUE}
fn_show_table_dynamic(object_name = "df_normality", caption_text = "")

```

## Requeriments - Residuals Homogeneity
```{r include=TRUE}
fn_show_table_dynamic(object_name = "df_homogeneity", caption_text = "")

```

\newpage

# Reporting Level I - Summary Anova

## Summary Table
```{r include=TRUE}
fn_show_table_dynamic(object_name = "df_summary_anova", caption_text = "")

```

<!-- ## Plot for Tukey -->
<!-- ```{r} -->
<!-- #| warning: false -->
<!-- #| echo: false -->
<!-- plot007_factor -->
<!-- ``` -->


## Phrases
```{r}
#| eval: true
#| include: false
#| warning: false
#| echo: false


# 
my_text <- c(phrase01_normality_selected, 
    phrase01_homogeneity_selected,
    phrase01A_requeriments_selected,
    phrase01B_requeriments_selected,
    phrase01C_requeriments_selected,
    phrase01_anova_selected,
    phrase01A_tukey_selected,
    phrase01B_tukey_selected,
    phrase01C_tukey_selected,
    phrase01_anova_tukey_selected)



```
`r my_text[1]`  
`r my_text[2]`  
`r my_text[3]`  
`r my_text[4]`
`r my_text[5]`
`r my_text[6]`
`r my_text[7]`
`r my_text[8]`
`r my_text[9]`
`r my_text[10]`



\newpage


# Reporting Level II - Decision-Making Process in ANOVA
The ANOVA test is specifically performed to make decisions.  
The decision-making process has a set of sequential steps, in a particular order.  
**Step 01:** Normality Verification  
**Step 02:** Homogeneity Verification  
**Step 03:** Global Requirements Check  
**Step 04:** ANOVA Validation  
**Step 05:** ANOVA Interpretation  
**Step 06:** Tukey Test Validation  
**Step 07:** Tukey Test Interpretation  
**Step 08:** ANOVA-Tukey Consistency Analysis  
**Step 09:** Final Conclusion


## **Step 01:** Normality Verification  
```{r}
#| warning: false
#| echo: false
fn_show_table_dynamic(object_name = "df_normality", caption_text = "")
```


```{r}
#| warning: false
#| echo: false
knitr::asis_output(phrase02_normality_selected)
```


## **Step 02:** Homogeneity Verification  

```{r}
#| warning: false
#| echo: false
fn_show_table_dynamic(object_name = "df_homogeneity", caption_text = "")
```

```{r}
#| warning: false
#| echo: false
knitr::asis_output(phrase02_homogeneity_selected)
```


## **Step 03:** Global Requirements Check  
```{r}
#| warning: false
#| echo: false


knitr::asis_output(phrase02A_requeriments_selected)
```

## **Step 04:** ANOVA Validation  
```{r}
#| warning: false
#| echo: false
knitr::asis_output(phrase02B_requeriments_selected)
knitr::asis_output(phrase02C_requeriments_selected)
```

  

## **Step 05:** ANOVA Interpretation  

```{r}
#| warning: false
#| echo: false
fn_show_table_dynamic(object_name = "df_table_anova_classroom", caption_text = "")
```

```{r}
#| warning: false
#| echo: false
knitr::asis_output(phrase02_anova_selected)
```



## **Step 06:** Tukey Test Validation  
```{r}
#| warning: false
#| echo: false

knitr::asis_output(phrase02A_tukey_selected)
knitr::asis_output(phrase02B_tukey_selected)

```

\newpage

## **Step 07:** Tukey Test Interpretation  

```{r}
#| warning: false
#| echo: false
knitr::asis_output(phrase02C_tukey_selected)
fn_show_table_dynamic(object_name = "df_tukey_table_classroom", caption_text = "")
plot007_factor
```


\newpage

## **Step 08:** ANOVA-Tukey Consistency Analysis  
```{r}
#| warning: false
#| echo: false


knitr::asis_output(phrase01_anova_tukey_selected)
```


```{r, eval=TRUE, include=TRUE, echo=FALSE}
knitr::asis_output("The means of each factor level are detailed with the standard error derived from the model.  
                   The statistical groups from the Tukey test are detailed for each factor level.")
```


\newpage

# Reporting Level III - Automatic Statistic Asesor (ASA)
## General
```{r, eval=TRUE, include=TRUE, echo=FALSE}

knitr::asis_output(text_asa_01_human)

```

## Requeriments

```{r, eval=TRUE, include=TRUE, echo=FALSE}

knitr::asis_output(text_asa_02_model_requeriments)

```

## Anova

```{r, eval=TRUE, include=TRUE, echo=FALSE}

knitr::asis_output(text_asa_03_anova)

```

## Tukey

```{r, eval=TRUE, include=TRUE, echo=FALSE}

knitr::asis_output(text_asa_04_tukey)

```






