---
title: "Rscience - Hidden Runner"
format: 
  html: 
    output-file: "AAA_lab01_action02_000_run_Rscript_internal_HIDDEN_RUNNER.html"
    embed-resources: true
    number-sections: true
    number-depth: 3
    include-in-header:
      text: |
        <style>
        h1, h2, .title {
          border-bottom: none !important;
          margin-bottom: 10px;
        }
        </style>
execute: 
  enabled: true
---

Tool: Rs003_LM_QQ_FIX_BAL_ANOVA_1Way_s001  
File name qmd: AAA_lab01_action02_000_run_Rscript_internal_HIDDEN_RUNNER.qmd
File name html: AAA_lab01_action02_000_run_Rscript_internal_HIDDEN_RUNNER.html


```{r step00_time_start, eval=TRUE, echo=FALSE, results='asis'}
# Captura del tiempo inicial
time_start <- Sys.time()

cat("<b>Runner Execution Started:</b>", format(time_start, "%Y-%m-%d %H:%M:%S"), "<br>")
cat("<hr>")
```


```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Libraries
library("fs")
library("knitr")
library("tidyverse")
library("kableExtra")

# Funtions
source(file = "../../pos02_00_action_fn/fn_actions.R")
```

---

```{r basics, eval=TRUE, echo=FALSE, results='asis'}
# Files
   str_file_stone_html <- "AAA_lab01_action02_000_run_Rscript_internal_HIDDEN_RUNNER.html"
   str_regex_remove_stone_qmd_files <- "_STONE.qmd$"
   
   vector_stone_files_qmd <- c("action02_lab01_step01_cleaning_STONE.qmd",
                           "action02_lab01_step02_run_Rscript_internal_STONE.qmd")
   
   vector_stone_files_html <- fs::path_ext_set(vector_stone_files_qmd, "html")
   
```

# Basics status and cleaning.
## Checking Hidden Runner HTML file at local folder.

::: {.callout-note}
File HTML hidden-runner must not exists or be deleted previous execution.
::: 
```{r step01_01_01, eval=TRUE, echo=FALSE, results='asis'}
step01_01_01 <- function(){
  # upgraded!
  the_output <- fn_delete_single_file(str_file_path = str_file_stone_html)
  if(!the_output) knitr::knit_exit()
}
step01_01_01()
```




# Checking all `r str_regex_remove_stone_qmd_files`
## All selected files are `r str_regex_remove_stone_qmd_files`

::: {.callout-note}
Must exists all .qmd files from actions.
:::
```{r step02_01_01, eval=TRUE, echo=FALSE, results='asis'}


step02_01_01 <- function(){
  
  the_output <- fn_check_multi_files_pattern(vector_paths = vector_stone_files_qmd, 
                                              str_regex = str_regex_remove_stone_qmd_files)
  if(!the_output) knitr::knit_exit()
}
step02_01_01()
```

## All selected files exists.

```{r step02_02_01, eval=TRUE, echo=FALSE, results='asis'}


step02_02_01 <- function(){
  
  the_output <- fn_check_multi_files(vector_paths = vector_stone_files_qmd)
  if(!the_output) knitr::knit_exit()
}
step02_02_01()
```

## Run quarto 
```{r step02_03_01, eval=TRUE, echo=FALSE, results='asis'}




step02_03_01 <- function(){
  the_output <- fn_render_qmd_files(vector_files = vector_stone_files_qmd)
  if(!the_output) knitr::knit_exit()
}
# Execute the step
step02_03_01()

```


# Final Summary
```{r step_final_time_end, eval=TRUE, echo=FALSE, results='asis'}
# 1. Cálculos de tiempo
time_end <- Sys.time()
time_duration <- difftime(time_end, time_start, units = "auto")
str_duration <- format(time_duration, digits = 3)



# 3. Construcción del HTML (Asegurando que no haya espacios extraños al inicio)
html_summary <- paste0(
  "<hr>",
  "<div style='background-color: #f8f9fa; border: 1px solid #dee2e6; padding: 15px; border-radius: 5px; font-family: sans-serif; color: #333;'>",
  "  <b style='display: block; color: #495057; font-size: 1.1em; margin-bottom: 10px;'>🏁 Final Execution Summary</b>",
  "  <div style='margin-bottom: 5px;'>🕒 <b>Start Time:</b> ", format(time_start, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>🏁 <b>End Time:&nbsp;</b> ", format(time_end, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>⌛ <b>Total Duration:</b> <span style='color: #007bff; font-weight: bold;'>", str_duration, "</span></div>",
  "</div>",
  "<div style='text-align: center; margin-top: 10px;'><small style='color: #6c757d;'>End of Rscience Automated Runner</small></div>"
)

# Usamos cat con fill = TRUE para asegurar que el buffer se limpie correctamente
cat(html_summary, fill = TRUE)
```
