---
title: "Rscience - Hidden Runner"
format: 
  html: 
    output-file: "action02_lab01_step02_run_Rscript_internal_STONE.html"
    embed-resources: true
    number-sections: true
    number-depth: 3
    include-in-header:
      text: |
        <style>
        h1, h2, .title {
          border-bottom: none !important;
          margin-bottom: 10px;
        }
        </style>
execute: 
  enabled: true
---

Tool: Rs003_LM_QQ_FIX_BAL_ANOVA_1Way_s001  
File name qmd: action02_lab01_step02_run_Rscript_internal_STONE.qmd
File name html: action02_lab01_step02_run_Rscript_internal_STONE.html


```{r step00_time_start, eval=TRUE, echo=FALSE, results='asis'}
# Captura del tiempo inicial
time_start <- Sys.time()

cat("<b>Runner Execution Started:</b>", format(time_start, "%Y-%m-%d %H:%M:%S"), "<br>")
cat("<hr>")
```


```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Libraries
library("fs")
library("knitr")
library("tidyverse")
library("kableExtra")

# Funtions
source(file = "../../pos02_00_action_fn/fn_actions.R")
```

---

```{r basics, eval=TRUE, echo=FALSE, results='asis'}
# Files
   str_file_stone_html <- "action02_lab01_step01_cleaning_STONE.html"
   str_regex_remove_html_files <- ".html$"
   str_file_name_Rscript_internal <- "zzz_output_action01_lab01_step04_Rscript_internal.R"
   str_file_name_RData_Rscript_internal <- "zzz_output_action02_lab01_step02_RData_internal.RData"
   
# Folders
   str_folder_output_local <- "zzz_output_local"
   str_folder_output_external <- "../../zzz_zzz_output"

# Paths
   str_Rscript_internal_path_LOCAL    <- file.path(str_folder_output_local, str_file_name_Rscript_internal)
   str_Rscript_internal_path_EXTERNAL    <- file.path(str_folder_output_external, str_file_name_Rscript_internal)

   
   str_RData_Rscript_internal_path_LOCAL    <- file.path(str_folder_output_local,  str_file_name_RData_Rscript_internal)
   str_RData_Rscript_internal_path_EXTERNAL   <- file.path(str_folder_output_external,  str_file_name_RData_Rscript_internal)

```

# Basics status and cleaning.
## Checking Stone HTML file at local folder.
::: {.callout-note}
File stone HTML must not exists or be deleted previous execution.
::: 
```{r step01_01_01, eval=TRUE, echo=FALSE, results='asis'}
step01_01_01 <- function(){
  
  the_output <- fn_delete_single_file(str_file_path = str_file_stone_html)
  if(!the_output) knitr::knit_exit()
}
step01_01_01()
```

## Checking output folder local.
::: {.callout-note}
Folder must exists.
::: 
```{r step01_04_01, eval=TRUE, echo=FALSE, results='asis'}
step01_04_01 <- function(){
  
  the_output <- fn_check_single_folder(str_folder_path = str_folder_output_local)
  if(!the_output) knitr::knit_exit()
}
step01_04_01()
```


## Copying for Rscript internal.
::: {.callout-note}
File Rscript internal must exists localy.  
We take the file from external output folder.
::: 
```{r step01_05_01, eval=TRUE, echo=FALSE, results='asis'}
step01_05_01 <- function(){
  
  the_output <- fn_check_single_file(str_file_path = str_Rscript_internal_path_EXTERNAL)
  if(!the_output) knitr::knit_exit()
}
step01_05_01()
```


```{r step01_05_02, eval=TRUE, echo=FALSE, results='asis'}
step01_05_02 <- function(){
  
  the_output <- fn_delete_single_file(str_file_path = str_Rscript_internal_path_LOCAL)
  if(!the_output) knitr::knit_exit()
}
step01_05_02()
```


```{r step01_05_03, eval=TRUE, echo=FALSE, results='asis'}
step01_05_03 <- function(){
  
  the_output <- fn_copy_verify_single_file(str_from = str_Rscript_internal_path_EXTERNAL, 
                                           str_to = str_Rscript_internal_path_LOCAL)
  if(!the_output) knitr::knit_exit()
}
step01_05_03()
```

## Cleaning ENV Rscript internal.
::: {.callout-note}
File ENV .RData from Rscript internal must be removed if exists.
::: 
```{r step01_06_01, eval=TRUE, echo=FALSE, results='asis'}
step01_06_01 <- function(){
  
  the_output <- fn_delete_single_file(str_file_path = str_RData_Rscript_internal_path_LOCAL)
  if(!the_output) knitr::knit_exit()
}
step01_06_01()
```




## Delete files from external output.
::: {.callout-note}
File .RData internal on the external output folder  must not exists or be deleted previous execution.

::: 
```{r step01_06_02, eval=TRUE, echo=FALSE, results='asis'}
step01_06_02 <- function(){
  # upgraded!
  the_output <- fn_delete_multi_files_SUPER_POWER(vector_file_paths = str_RData_Rscript_internal_path_EXTERNAL)
  if(!the_output) knitr::knit_exit()
}
step01_06_02()
```


# Running Rscript internal
```{r step02_01_01, eval=TRUE, echo=FALSE, results='asis'}
step02_01_01 <- function(){
  
    # 1. Definir rutas
    script_path <- str_Rscript_internal_path_LOCAL
    RData_output_path <- str_RData_Rscript_internal_path_LOCAL
    
    # 2. Crear un nuevo entorno vacío
    script_env <- new.env()
    
    # 3. Ejecución Silenciosa y Controlada
    cat(paste0("<b>Executing Internal Script:</b> <code>", fs::path_file(script_path), "</code><br>"))
    cat("<small style='color: #6c757d; font-style: italic;'>Action: Running isolated process and capturing environment.</small><br>")
    
    exec_result <- tryCatch({
      # Silenciamos cat(), print(), mensajes de carga y advertencias
      capture.output({
        suppressMessages(suppressWarnings({
          sys.source(script_path, envir = script_env)
        }))
      })
      TRUE # Retorno si todo sale bien
    }, error = function(e) {
      return(e$message) # Retorno del mensaje de error si falla
    })
    
    # 4. Verificación y Guardado
    if (isTRUE(exec_result)) {
      # Guardar solo si la ejecución fue exitosa
      save(list = ls(script_env), envir = script_env, file = RData_output_path)
      
      cat(paste0("<span style='color: #28a745;'>✔ <b>Success:</b> Environment exported to <code>", RData_output_path, "</code></span><br><br>"))
      
      # 5. Validación final del archivo físico
      the_output <- fn_check_single_file(str_file_path = RData_output_path)
      if(!the_output) knitr::knit_exit()
    
    } else {
      # Reporte de error estético
      cat("<span style='color: #dc3545;'>✘ <b>Runtime Error:</b> The script failed to complete.</span><br>")
      cat(paste0("<div style='background-color: #fff5f5; border-left: 3px solid #dc3545; padding: 8px; margin-top: 5px;'>",
                 "<small style='color: #b02a37;'><b>Technical Detail:</b> ", exec_result, "</small></div><br>"))
      knitr::knit_exit()
    }
    
  # the_output <- fn_delete_single_file(str_file_target = str_RData_ENV_internal_file_path)
  # if(!the_output) knitr::knit_exit()
}
step02_01_01()
```



# Export zzz_output files and folders.
```{r step_export, eval=TRUE, echo=FALSE, results='asis'}
the_output <- fn_export_files_zzz_output(str_path_from = str_folder_output_local, 
                                         str_path_to = str_folder_output_external,
                                         bln_overwrite = FALSE,
                                         bln_production = TRUE)
if(!the_output) knitr::knit_exit()
```



# Final Summary
```{r step_final_time_end, eval=TRUE, echo=FALSE, results='asis'}
# 1. Cálculos de tiempo
time_end <- Sys.time()
time_duration <- difftime(time_end, time_start, units = "auto")
str_duration <- format(time_duration, digits = 3)



# 3. Construcción del HTML (Asegurando que no haya espacios extraños al inicio)
html_summary <- paste0(
  "<hr>",
  "<div style='background-color: #f8f9fa; border: 1px solid #dee2e6; padding: 15px; border-radius: 5px; font-family: sans-serif; color: #333;'>",
  "  <b style='display: block; color: #495057; font-size: 1.1em; margin-bottom: 10px;'>🏁 Final Execution Summary</b>",
  "  <div style='margin-bottom: 5px;'>🕒 <b>Start Time:</b> ", format(time_start, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>🏁 <b>End Time:&nbsp;</b> ", format(time_end, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>⌛ <b>Total Duration:</b> <span style='color: #007bff; font-weight: bold;'>", str_duration, "</span></div>",
  "</div>",
  "<div style='text-align: center; margin-top: 10px;'><small style='color: #6c757d;'>End of Rscience Automated Runner</small></div>"
)

# Usamos cat con fill = TRUE para asegurar que el buffer se limpie correctamente
cat(html_summary, fill = TRUE)
```

