

### Decision-Making Process in ANOVA
The ANOVA test is specifically performed to make decisions.  
The decision-making process has a set of sequential steps, in a particular order.  
**Step 01:** Normality Verification  
**Step 02:** Homogeneity Verification  
**Step 03:** Global Requirements Check  
**Step 04:** ANOVA Validation  
**Step 05:** ANOVA Interpretation  
**Step 06:** Tukey Test Validation  
**Step 07:** Tukey Test Interpretation  
**Step 08:** ANOVA-Tukey Consistency Analysis  
**Step 09:** Final Conclusion

<div style="background-color: #e8f4fd; padding: 1.5rem; margin-bottom: 1rem; border-left: 4px solid #007bff; border-radius: 4px;">
**Step 01:** Normality Verification  
::: {.columns}
::: {.column width="48%"}
```{r}
#| warning: false
#| echo: false
fn_show_table_dynamic(object_name = "df_normality", caption_text = "")
```
:::
::: {.column width="4%"}
:::
::: {.column width="48%"}
```{r}
#| warning: false
#| echo: false
knitr::asis_output(phrase02_normality_selected)
```
:::
:::
</div>

<!-- <hr style="border: 1px solid #dee2e6; margin: 1rem 0;">  -->

<div style="background-color: #e8f4fd; padding: 1.5rem; margin-bottom: 1rem; border-left: 4px solid #007bff; border-radius: 4px;">
**Step 02:** Homogeneity Verification  
::: {.columns}
::: {.column width="48%"}
```{r}
#| warning: false
#| echo: false
fn_show_table_dynamic(object_name = "df_homogeneity", caption_text = "")
```
:::
::: {.column width="4%"}
:::
::: {.column width="48%"}
```{r}
#| warning: false
#| echo: false
knitr::asis_output(phrase02_homogeneity_selected)
```
:::
:::
</div>


<div style="background-color: #e8f4fd; padding: 1.5rem; margin-bottom: 1rem; border-left: 4px solid #007bff; border-radius: 4px;">
**Step 03:** Global Requirements Check  
```{r}
#| warning: false
#| echo: false


knitr::asis_output(phrase02A_requeriments_selected)
```
</div>


<div style="background-color: #e8f4fd; padding: 1.5rem; margin-bottom: 1rem; border-left: 4px solid #007bff; border-radius: 4px;">
**Step 04:** ANOVA Validation  
```{r}
#| warning: false
#| echo: false
knitr::asis_output(phrase02B_requeriments_selected)
knitr::asis_output(phrase02C_requeriments_selected)
```
</div>


<div style="background-color: #e8f4fd; padding: 1.5rem; margin-bottom: 1rem; border-left: 4px solid #007bff; border-radius: 4px;">
**Step 05:** ANOVA Interpretation  
::: {.columns}
::: {.column width="53%"}
```{r}
#| warning: false
#| echo: false
fn_show_table_dynamic(object_name = "df_table_anova_classroom", caption_text = "")
```
:::
::: {.column width="4%"}
:::
::: {.column width="43%"}
```{r}
#| warning: false
#| echo: false
knitr::asis_output(phrase02_anova_selected)
```
:::
:::
</div>


<div style="background-color: #e8f4fd; padding: 1.5rem; margin-bottom: 1rem; border-left: 4px solid #007bff; border-radius: 4px;">
**Step 06:** Tukey Test Validation  
```{r}
#| warning: false
#| echo: false

knitr::asis_output(phrase02A_tukey_selected)
knitr::asis_output(phrase02B_tukey_selected)

```
</div>


<div style="background-color: #e8f4fd; padding: 1.5rem; margin-bottom: 1rem; border-left: 4px solid #007bff; border-radius: 4px;">
**Step 07:** Tukey Test Interpretation  
::: {.columns}
::: {.column width="100%"}
```{r}
#| warning: false
#| echo: false
knitr::asis_output(phrase02C_tukey_selected)
fn_show_table_dynamic(object_name = "df_tukey_table_classroom", caption_text = "")
plot007_factor
```
:::
:::
</div>


<div style="background-color: #e8f4fd; padding: 1.5rem; margin-bottom: 1rem; border-left: 4px solid #007bff; border-radius: 4px;">
**Step 08:** ANOVA-Tukey Consistency Analysis  
```{r}
#| warning: false
#| echo: false


knitr::asis_output(phrase01_anova_tukey_selected)
```


```{r, eval=TRUE, include=TRUE, echo=FALSE}
knitr::asis_output("The means of each factor level are detailed with the standard error derived from the model.  
                   The statistical groups from the Tukey test are detailed for each factor level.")
```
</div>

