\  

The most important statistical output from Anova as R formatted objects.  
\  

::: {.panel-tabset}
<!-- ## Model -->
<!-- ```{r code04_01, child='file00_04_ClassRoom_01_model.qmd'} -->
<!-- ``` -->

<!-- ## Hypothesis -->
<!-- ```{r code04_02, child='file00_04_ClassRoom_02_hypothesis.qmd'} -->
<!-- ``` -->

## User election
### Selected variable and rol
```{r}
#| echo: false
fn_show_table_dynamic(object_name = "df_selected_vars", caption_text = "")
```

### Alpha and confidence values
```{r}
#| echo: false

fn_show_table_dynamic(object_name = "df_alpha_confidence", caption_text = "")
```

### Amount of data to analysis
```{r}
#| echo: false

fn_show_table_dynamic(object_name = "df_show_n", caption_text = "")
```


## Anova Table

### 1) Anova Table (Class Room format)
```{r}
#| echo: false
knitr::asis_output("This is the table format detailed in the bibliography.")

fn_show_table_dynamic(object_name = "df_table_anova_classroom", caption_text = "")
```


### 2) Anova Table (R format)
```{r}
#| echo: false
knitr::asis_output("The original R output does not contain the Source of Variation column, and it does not detail the row for the total source of variation.")

fn_show_table_dynamic(object_name = "df_table_anova", caption_text = "")
```






## Tukey Test

### 1) Tukey Test (Class Room format)
```{r}
#| echo: false
knitr::asis_output("This is the table format detailed in the bibliography.")

fn_show_table_dynamic(object_name = "df_tukey_table_classroom", caption_text = "")
```

### 2) Special plot for Tukey test
```{r}
#| echo: false
knitr::asis_output("The means of each factor level are detailed with the standard error derived from the model.  
                   The statistical groups from the Tukey test are detailed for each factor level.")
```
```{r}
#| echo: false

plot007_factor
```

### 3) Full info from Tukey (R format)
```{r}
#| echo: false
knitr::asis_output("The Tukey table is only one part of all the information contained within the Tukey test.  
                   The Tukey test contains more details that may be relevant, such as the honest significant difference (HSD).")

```
```{r}
#| echo: false
tukey01_full_groups
```

### 4) Pairs comparation from Tukey test (R format)
```{r}
#| echo: false
knitr::asis_output("Internally, the Tukey test performs t-tests between all possible pairs of factor levels.  
                   In each t-test, a p-value is obtained with which decisions are made. All pairs are detailed below.")
```
```{r}
#| echo: false
tukey02_full_pairs
```






## Requeriments
```{r code04_03, child='file00_04_ClassRoom_03_requeriments.qmd'}
```
## Plots - Raw Data
```{r code04_04, child='file00_04_ClassRoom_04_data_raw_plots.qmd'}
```
## Plots - Residuals
```{r code04_05, child='file00_04_ClassRoom_05_residuals_raw_plots.qmd'}
```

<!-- ## Decision Plan -->
<!-- ```{r code04_06, child='file00_04_ClassRoom_06_decision_plan.qmd'} -->
<!-- ``` -->



## FAQs
```{r code04_08, child='file00_04_ClassRoom_08_FAQ.qmd'}
```

:::
