---
title: "Rscience - Hidden Runner"
format: 
  html: 
    output-file: "report01_lab01_step01_cleaning_RUN_HIDDEN.html"
    embed-resources: true
    number-sections: true
    number-depth: 3
    include-in-header:
      text: |
        <style>
        h1, h2, .title {
          border-bottom: none !important;
          margin-bottom: 10px;
        }
        </style>
execute: 
  enabled: true
---

Tool: Rs003_LM_QQ_FIX_BAL_ANOVA_1Way_s001  
File name qmd: report01_lab01_step01_cleaning_RUN_HIDDEN.qmd
File name html: report01_lab01_step01_cleaning_RUN_HIDDEN.html


```{r step00_time_start, eval=TRUE, echo=FALSE, results='asis'}
# Captura del tiempo inicial
time_start <- Sys.time()

cat("<b>Runner Execution Started:</b>", format(time_start, "%Y-%m-%d %H:%M:%S"), "<br>")
cat("<hr>")
```


```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Libraries
library("fs")
library("knitr")
library("tidyverse")
library("kableExtra")

# Funtions
source(file = "fn_local.R")
source(file = "fn_actions.R")
```

---

```{r basics, eval=TRUE, echo=FALSE, results='asis'}
# Files
   str_file_hidder_runner_html <- "report01_lab01_step01_cleaning_RUN_HIDDEN.html"
   str_regex_remove_runners_files <- "_RUN_HIDDEN.html$"
# Folders
   str_folder_input_external_lab00 <- "../lab00_HIDDEN_original_RQuarto"
   str_folder_output_local <- "zzz_output_local"
   str_folder_output_external <- "../../zzz_zzz_output"
   
```

# Basics status and cleaning.
## Checking Hidden Runner HTML file at local folder.

::: {.callout-note}
File HTML hidden-runner must not exists or be deleted previous execution.
::: 
```{r step01_01_01, eval=TRUE, echo=FALSE, results='asis'}
step01_01_01 <- function(){
  
  the_output <- fn_delete_single_file(str_file_target = str_file_hidder_runner_html)
  if(!the_output) knitr::knit_exit()
}
step01_01_01()
```

## Deleting all "RUNNER_HIDDEN.html" from folder.
::: {.callout-caution}
The cleanning for <code> RUNNER_HIDDEN.html </code> only ocurred here.  
Will not happen in any other runner.  
Happen here becouse is the first runner.
:::

```{r step01_01_02, eval=TRUE, echo=FALSE, results='asis'}
step01_01_02 <- function(){
  
  vector_path_runners <- fs::dir_ls(path = ".", regexp = str_regex_remove_runners_files)
  # list_runners
  the_output <- fn_delete_multi_files(vector_paths = vector_path_runners)
  if(!the_output) knitr::knit_exit()
}
step01_01_02()
```

---

## External folder "lab00" must exists.
::: {.callout-note}
Must exists a <code>`r str_folder_input_external_lab00`</code>.  
From lab00 we will take all the originals .qmd files.
::: 

```{r step01_02_01, eval=TRUE, echo=FALSE, results='asis'}
step01_02_01 <- function(){
  
  the_output <- fn_check_single_folder(str_folder_target = str_folder_input_external_lab00)
  if(!the_output) knitr::knit_exit()
}
step01_02_01()
```

---


## Output local folder.

::: {.callout-note}
Must exists a <code>`r str_folder_output_local`</code> at local folder and must be empty before render files.
::: 

```{r step01_03_01, eval=TRUE, echo=FALSE, results='asis'}
step01_03_01 <- function(){
  
  the_output <- fn_check_single_folder(str_folder_target = str_folder_output_local)
  if(!the_output) knitr::knit_exit()
}
step01_03_01()
```


```{r step01_03_02, eval=TRUE, echo=FALSE, results='asis'}
step01_03_02 <- function(){
  
  the_output <- fn_cleaning_single_folder(str_folder_target = str_folder_output_local)
  if(!the_output) knitr::knit_exit()
}
step01_03_02()
```



---

## Output external folder.

::: {.callout-note}
Must exists a <code> `r str_folder_output_external` </code> at local folder and must be empty before render files.
::: 

```{r step01_03_0199, eval=TRUE, echo=FALSE, results='asis'}
step01_03_01 <- function(){
  
  the_output <- fn_check_single_folder(str_folder_target = str_folder_output_external)
  if(!the_output) knitr::knit_exit()
}
step01_03_01()
```

::: {.callout-caution}
The cleanning for <code> `r str_folder_output_external` </code> only ocurred here.  
Will not happen in any other runner.  
Happen here becouse is the first runner.
:::
```{r step01_03_0299, eval=TRUE, echo=FALSE, results='asis'}
step01_03_02 <- function(){
  
  the_output <- fn_cleaning_single_folder(str_folder_target = str_folder_output_external)
  if(!the_output) knitr::knit_exit()
}
step01_03_02()
```



# Final Summary
```{r step_final_time_end, eval=TRUE, echo=FALSE, results='asis'}
# 1. Cálculos de tiempo
time_end <- Sys.time()
time_duration <- difftime(time_end, time_start, units = "auto")
str_duration <- format(time_duration, digits = 3)



# 3. Construcción del HTML (Asegurando que no haya espacios extraños al inicio)
html_summary <- paste0(
  "<hr>",
  "<div style='background-color: #f8f9fa; border: 1px solid #dee2e6; padding: 15px; border-radius: 5px; font-family: sans-serif; color: #333;'>",
  "  <b style='display: block; color: #495057; font-size: 1.1em; margin-bottom: 10px;'>🏁 Final Execution Summary</b>",
  "  <div style='margin-bottom: 5px;'>🕒 <b>Start Time:</b> ", format(time_start, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>🏁 <b>End Time:&nbsp;</b> ", format(time_end, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>⌛ <b>Total Duration:</b> <span style='color: #007bff; font-weight: bold;'>", str_duration, "</span></div>",
  "</div>",
  "<div style='text-align: center; margin-top: 10px;'><small style='color: #6c757d;'>End of Rscience Automated Runner</small></div>"
)

# Usamos cat con fill = TRUE para asegurar que el buffer se limpie correctamente
cat(html_summary, fill = TRUE)
```
