---
title: "Rscience - Hidden Runner"
format: 
  html: 
    output-file: "report01_lab01_step03_apply_user_selection_RUN_HIDDEN.html"
    embed-resources: true
    number-sections: true
    number-depth: 3
    include-in-header:
      text: |
        <style>
        h1, h2, .title {
          border-bottom: none !important;
          margin-bottom: 10px;
        }
        </style>
execute: 
  enabled: true
---

Tool: Rs003_LM_QQ_FIX_BAL_ANOVA_1Way_s001  
File name qmd: report01_lab01_step03_apply_user_selection_RUN_HIDDEN.qmd
File name html: report01_lab01_step03_apply_user_selection_RUN_HIDDEN.html


```{r step00_time_start, eval=TRUE, echo=FALSE, results='asis'}
# Captura del tiempo inicial
time_start <- Sys.time()

cat("<b>Runner Execution Started:</b>", format(time_start, "%Y-%m-%d %H:%M:%S"), "<br>")
cat("<hr>")
```


```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Libraries
library("fs")
library("knitr")
library("tidyverse")
library("kableExtra")

# Funtions
source(file = "fn_local.R")
source(file = "fn_actions.R")
```

---

```{r basics, eval=TRUE, echo=FALSE, results='asis'}
# Files
   str_file_hidder_runner_html <- "report01_lab01_step03_apply_user_selection_RUN_HIDDEN.html"
   str_qmd_original <- "report01_lab00_original_RQuarto_01_ANOVA.qmd"
   str_qmd_CopyMod <-  "report01_lab01_step03_CopyMod_RQuarto_01_ANOVA.qmd"

# Folders
   str_folder_input_external_lab00 <- "../lab00_HIDDEN_original_RQuarto"
   str_folder_output_local <- "zzz_output_local"

# Paths 
   str_file_path_original <- fs::path(str_folder_output_local, str_qmd_original)
   str_file_path_CopyMod  <- fs::path(str_folder_output_local, str_qmd_CopyMod)


```

# Basics status and cleaning.
## Checking Hidden Runner HTML file at local folder.
::: {.callout-note}
File HTML hidden-runner must not exists or be deleted previous execution.
::: 
```{r step01_01_01, eval=TRUE, echo=FALSE, results='asis'}
step01_01_01 <- function(){
  
  the_output <- fn_delete_single_file(str_file_target = str_file_hidder_runner_html)
  if(!the_output) knitr::knit_exit()
}
step01_01_01()
```

## CopyMod qmd file, reset.
::: {.callout-note}
File qmd CopyMod, is deleted if exist to start from zero.
::: 
```{r step01_02_01, eval=TRUE, echo=FALSE, results='asis'}
step01_02_01 <- function(){
  
  the_output <- fn_delete_single_file(str_file_target = str_file_path_CopyMod)
  if(!the_output) knitr::knit_exit()
}
step01_02_01()
```

## Orignal qmd, must exists.
::: {.callout-note}
Original qmd file must exists.
::: 
```{r step01_03_01, eval=TRUE, echo=FALSE, results='asis'}
step01_03_01 <- function(){

  the_output <- fn_check_single_file(str_file_path = str_file_path_original)
  if(!the_output) knitr::knit_exit()
}
step01_03_01()
```
---


# Copying files FROM-TO.
::: {.callout-note}
Copying the original qmd file in a new copy with a diferent name  with "CopyMod".

:::

```{r step02_05_01, eval=TRUE, echo=FALSE, results='asis'}


step02_05_01 <- function(){
  
the_output <- fn_copy_verify_single_file(str_from = str_file_path_original, 
                                          str_to = str_file_path_CopyMod)
if(!the_output) knitr::knit_exit()
}
step02_05_01()
```




```{r step03_01_02, rename_process, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
step03_01_02 <- function(){
the_output <- fn_check_single_file(str_file_path = str_file_path_CopyMod)
if(!the_output) knitr::knit_exit()
}
step03_01_02()
```



# Modifiying qmd copy file
::: {.callout-note}
Now, we will apply the substituions about \_\_MY_OBJ\_\_ on the script.

:::



```{r  step04_01_02, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

step04_01_02 <- function(){
  

    vector_lines <- readLines(str_file_path_CopyMod, warn = FALSE, encoding = "UTF-8")
    pattern_to_find <- "__.*?__"
    
    # --- PASO A: DETECCIÓN INICIAL ---
    vector_pos_init   <- grep(pattern_to_find, vector_lines)
    total_matches_init <- length(vector_pos_init)
    
    cat(paste0("<b>Step 1 - Initial Scan:</b> Found <code>", total_matches_init, "</code> lines to modify.<br>"))
    
    if (total_matches_init > 0) {
      
      # --- PASO B: TRANSFORMACIÓN OPTIMIZADA ---
      # Solo trabajamos sobre las líneas que tienen el patrón (más rápido)
      lines_to_modify <- vector_lines[vector_pos_init]
      
      lines_to_modify <- gsub('__import_external_my_dataset__', 'get("mtcars")', lines_to_modify)
      lines_to_modify <- gsub('__import_internal_my_dataset__', 'get("mtcars")', lines_to_modify)
      lines_to_modify <- gsub('__var_name_rv__', '"mpg"', lines_to_modify)
      lines_to_modify <- gsub('__var_name_factor__', '"cyl"', lines_to_modify)
      lines_to_modify <- gsub('__alpha_value__', '0.05', lines_to_modify)
      lines_to_modify <- gsub('__vector_ordered_levels__', 'c("8", "4", "6")', lines_to_modify)
      lines_to_modify <- gsub('__vector_ordered_colors__', 'c("#FF0000", "#00FF00", "#0000FF")', lines_to_modify)
      
      # Reinsertamos las líneas modificadas en el vector original
      vector_lines[vector_pos_init] <- lines_to_modify
      
      # --- PASO C: VERIFICACIÓN EN MEMORIA ---
      total_matches_mem <- length(grep(pattern_to_find, vector_lines))
      
      if (total_matches_mem == 0) {
        cat("<span style='color: #28a745;'>✔ <b>Success:</b> All patterns replaced in memory.</span><br>")
      } else {
        cat(paste0("<span style='color: #dc3545;'>✘ <b>Error:</b> ", total_matches_mem, " patterns still remain in memory.</span><br>"))
      }
    
      # --- PASO D: GUARDADO Y VERIFICACIÓN DE DISCO ---
      writeLines(text = vector_lines, con = str_file_path_CopyMod, useBytes = TRUE)
      
      # Re-leemos para estar 100% seguros de que el archivo en disco está limpio
      vector_lines_disk <- readLines(str_file_path_CopyMod, warn = FALSE, encoding = "UTF-8")
      total_matches_final <- length(grep(pattern_to_find, vector_lines_disk))
      
      if (total_matches_final == 0) {
        cat("<span style='color: #28a745;'>✔ <b>Success:</b> File saved and verified on disk (0 placeholders left).</span><br>")
      } else {
        cat(paste0("<span style='color: #dc3545;'>✘ <b>Critical Error:</b> File on disk still contains ", total_matches_final, " placeholders.</span><br>"))
      }
    
    } else {
      cat("<span style='color: #6c757d;'>ℹ <b>Info:</b> No placeholders found. No changes needed.</span><br>")
    }

}
step04_01_02()
```


# Final Summary
```{r step_final_time_end, eval=TRUE, echo=FALSE, results='asis'}
# 1. Cálculos de tiempo
time_end <- Sys.time()
time_duration <- difftime(time_end, time_start, units = "auto")
str_duration <- format(time_duration, digits = 3)



# 3. Construcción del HTML (Asegurando que no haya espacios extraños al inicio)
html_summary <- paste0(
  "<hr>",
  "<div style='background-color: #f8f9fa; border: 1px solid #dee2e6; padding: 15px; border-radius: 5px; font-family: sans-serif; color: #333;'>",
  "  <b style='display: block; color: #495057; font-size: 1.1em; margin-bottom: 10px;'>🏁 Final Execution Summary</b>",
  "  <div style='margin-bottom: 5px;'>🕒 <b>Start Time:</b> ", format(time_start, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>🏁 <b>End Time:&nbsp;</b> ", format(time_end, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>⌛ <b>Total Duration:</b> <span style='color: #007bff; font-weight: bold;'>", str_duration, "</span></div>",
  "</div>",
  "<div style='text-align: center; margin-top: 10px;'><small style='color: #6c757d;'>End of Rscience Automated Runner</small></div>"
)

# Usamos cat con fill = TRUE para asegurar que el buffer se limpie correctamente
cat(html_summary, fill = TRUE)
```
