---
title: "Rscience - Hidden Runner"
format: 
  html: 
    output-file: "report01_lab01_step06_render_RQuarto_RUN_HIDDEN.html"
    embed-resources: true
    number-sections: true
    number-depth: 3
    include-in-header:
      text: |
        <style>
        h1, h2, .title {
          border-bottom: none !important;
          margin-bottom: 10px;
        }
        </style>
execute: 
  enabled: true
---

Tool: Rs003_LM_QQ_FIX_BAL_ANOVA_1Way_s001  
File name qmd: report01_lab01_step06_render_RQuarto_RUN_HIDDEN.qmd
File name html: report01_lab01_step06_render_RQuarto_RUN_HIDDEN.html


```{r step00_time_start, eval=TRUE, echo=FALSE, results='asis'}
# Captura del tiempo inicial
time_start <- Sys.time()

cat("<b>Runner Execution Started:</b>", format(time_start, "%Y-%m-%d %H:%M:%S"), "<br>")
cat("<hr>")
```


```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Libraries
library("fs")
library("knitr")
library("tidyverse")
library("kableExtra")

# Funtions
source(file = "fn_local.R")
source(file = "fn_actions.R")
```

---

```{r basics, eval=TRUE, echo=FALSE, results='asis'}
# Files
    str_file_hidder_runner_html <- "report01_lab01_step06_render_RQuarto_RUN_HIDDEN.html"
    str_RQuarto_qmd_file <-  "report01_lab01_step03_CopyMod_RQuarto_01_ANOVA.qmd"
    str_RQuarto_html_old_file <- fs::path_ext_set(str_RQuarto_qmd_file, "html")
    
    str_RQuarto_html_new_file <- paste0("zzz_output_", str_RQuarto_html_old_file)
    str_RQuarto_html_new_file <- gsub("step03", "step06", str_RQuarto_html_new_file)

# Folders
    str_folder_output_local <- "zzz_output_local"
    str_folder_output_external <- "../../zzz_zzz_output"
    
# Paths 
    str_RQuarto_qmd_path  <- file.path(str_folder_output_local, str_RQuarto_qmd_file)
    str_RQuarto_html_old_path  <- file.path(str_folder_output_local, str_RQuarto_html_old_file)
    str_RQuarto_html_new_path  <- file.path(str_folder_output_local, str_RQuarto_html_new_file)


```

# Basics status and cleaning.
## Checking Hidden Runner HTML file at local folder.
::: {.callout-note}
File HTML hidden-runner must not exists or be deleted previous execution.
::: 
```{r step01_01_01, eval=TRUE, echo=FALSE, results='asis'}
step01_01_01 <- function(){
  
  the_output <- fn_delete_single_file(str_file_target = str_file_hidder_runner_html)
  if(!the_output) knitr::knit_exit()
}
step01_01_01()
```

## Checking for RQuarto qmd file.
::: {.callout-note}
File qmd initial must exists.
::: 
```{r step01_02_01, eval=TRUE, echo=FALSE, results='asis'}
step01_02_01 <- function(){
  
  the_output <- fn_check_single_file(str_file_path = str_RQuarto_qmd_path)
  if(!the_output) knitr::knit_exit()
}
step01_02_01()
```

## Checking output folder local.
::: {.callout-note}
Folder must exists.
::: 
```{r step01_03_01, eval=TRUE, echo=FALSE, results='asis'}
step01_03_01 <- function(){
  
  the_output <- fn_check_single_folder(str_folder_target = str_folder_output_local)
  if(!the_output) knitr::knit_exit()
}
step01_03_01()
```

## Checking output folder external.
::: {.callout-note}
Folder output external must exists.
::: 
```{r step01_04_01, eval=TRUE, echo=FALSE, results='asis'}
step01_04_01 <- function(){
  
  the_output <- fn_check_single_folder(str_folder_target = str_folder_output_external)
  if(!the_output) knitr::knit_exit()
}
step01_04_01()
```




# Rendering RQuarto 
```{r step02_01_01, eval=TRUE, echo=FALSE, results='asis'}
step02_01_01 <- function(){
  
  library("quarto")
    # str_RQuarto_html_old_path
  quarto::quarto_render(input = str_RQuarto_qmd_path, 
                        execute_dir = dirname(str_RQuarto_html_old_path), 
                        quiet = T)
  
  the_output <- fn_check_single_file(str_file_path = str_RQuarto_html_old_path)
  if(!the_output) knitr::knit_exit()
    
  the_output <- fn_rename_single_file(str_path_from = str_RQuarto_html_old_path, 
                                      str_path_to = str_RQuarto_html_new_path)

  if(!the_output) knitr::knit_exit()
}
step02_01_01()
```


# Export zzz_output files and folders.
```{r step_export, eval=TRUE, echo=FALSE, results='asis'}
the_output <- fn_export_files_zzz_output(str_path_from = str_folder_output_local, 
                                         str_path_to = str_folder_output_external,
                                         bln_overwrite = FALSE,
                                         bln_production = TRUE)
if(!the_output) knitr::knit_exit()
```


# Final Summary
```{r step_final_time_end, eval=TRUE, echo=FALSE, results='asis'}
# 1. Cálculos de tiempo
time_end <- Sys.time()
time_duration <- difftime(time_end, time_start, units = "auto")
str_duration <- format(time_duration, digits = 3)



# 3. Construcción del HTML (Asegurando que no haya espacios extraños al inicio)
html_summary <- paste0(
  "<hr>",
  "<div style='background-color: #f8f9fa; border: 1px solid #dee2e6; padding: 15px; border-radius: 5px; font-family: sans-serif; color: #333;'>",
  "  <b style='display: block; color: #495057; font-size: 1.1em; margin-bottom: 10px;'>🏁 Final Execution Summary</b>",
  "  <div style='margin-bottom: 5px;'>🕒 <b>Start Time:</b> ", format(time_start, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>🏁 <b>End Time:&nbsp;</b> ", format(time_end, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>⌛ <b>Total Duration:</b> <span style='color: #007bff; font-weight: bold;'>", str_duration, "</span></div>",
  "</div>",
  "<div style='text-align: center; margin-top: 10px;'><small style='color: #6c757d;'>End of Rscience Automated Runner</small></div>"
)

# Usamos cat con fill = TRUE para asegurar que el buffer se limpie correctamente
cat(html_summary, fill = TRUE)
```

