---
title: "Rscience - Hidden Runner"
format: 
  html: 
    output-file: "report01_lab01_step05_run_Rscript_internal_RUN_HIDDEN.html"
    embed-resources: true
    number-sections: true
    number-depth: 3
    include-in-header:
      text: |
        <style>
        h1, h2, .title {
          border-bottom: none !important;
          margin-bottom: 10px;
        }
        </style>
execute: 
  enabled: true
---

Tool: Rs003_LM_QQ_FIX_BAL_ANOVA_1Way_s001  
File name qmd: report01_lab01_step05_run_Rscript_internal_RUN_HIDDEN.qmd
File name html: report01_lab01_step05_run_Rscript_internal_RUN_HIDDEN.html


```{r step00_time_start, eval=TRUE, echo=FALSE, results='asis'}
# Captura del tiempo inicial
time_start <- Sys.time()

cat("<b>Runner Execution Started:</b>", format(time_start, "%Y-%m-%d %H:%M:%S"), "<br>")
cat("<hr>")
```


```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Libraries
library("fs")
library("knitr")
library("tidyverse")
library("kableExtra")

# Funtions
source(file = "fn_local.R")
source(file = "fn_actions.R")
```

---

```{r basics, eval=TRUE, echo=FALSE, results='asis'}
# Files
    str_file_hidder_runner_html <- "report01_lab01_step05_run_Rscript_internal_RUN_HIDDEN.html"
    str_R_script_file_name_internal <-  "zzz_output_report01_lab01_step04_Rscript_internal.R"
    str_RData_ENV_internal_file_name <- "zzz_output_report01_lab01_step05_ENV_Rscript_internal.RData"

# Folders
    str_folder_output_local <- "zzz_output_local"
    str_folder_output_external <- "../../zzz_zzz_output"
    
# Paths 
    str_R_script_file_path_internal  <- file.path(str_folder_output_local, str_R_script_file_name_internal)
    str_RData_ENV_internal_file_path <- file.path(str_folder_output_local, str_RData_ENV_internal_file_name)


```

# Basics status and cleaning.
## Checking Hidden Runner HTML file at local folder.
::: {.callout-note}
File HTML hidden-runner must not exists or be deleted previous execution.
::: 
```{r step01_01_01, eval=TRUE, echo=FALSE, results='asis'}
step01_01_01 <- function(){
  
  the_output <- fn_delete_single_file(str_file_target = str_file_hidder_runner_html)
  if(!the_output) knitr::knit_exit()
}
step01_01_01()
```

## Checking for Rscript internal.
::: {.callout-note}
File Rscript internal must exists.
::: 
```{r step01_02_01, eval=TRUE, echo=FALSE, results='asis'}
step01_02_01 <- function(){
  
  the_output <- fn_check_single_file(str_file_path = str_R_script_file_path_internal)
  if(!the_output) knitr::knit_exit()
}
step01_02_01()
```

## Cleaning ENV Rscript internal.
::: {.callout-note}
File ENV .RData from Rscript internal must be removed if exists.
::: 
```{r step01_03_01, eval=TRUE, echo=FALSE, results='asis'}
step01_03_01 <- function(){
  
  the_output <- fn_delete_single_file(str_file_target = str_RData_ENV_internal_file_path)
  if(!the_output) knitr::knit_exit()
}
step01_03_01()
```

## Checking output folder local.
::: {.callout-note}
Folder must exists.
::: 
```{r step01_04_01, eval=TRUE, echo=FALSE, results='asis'}
step01_04_01 <- function(){
  
  the_output <- fn_check_single_folder(str_folder_target = str_folder_output_local)
  if(!the_output) knitr::knit_exit()
}
step01_04_01()
```

## Checking output folder external.
::: {.callout-note}
Folder output external must exists.
::: 
```{r step01_05_01, eval=TRUE, echo=FALSE, results='asis'}
step01_05_01 <- function(){
  
  the_output <- fn_check_single_folder(str_folder_target = str_folder_output_external)
  if(!the_output) knitr::knit_exit()
}
step01_05_01()
```


# Running Rscript internal
```{r step02_01_01, eval=TRUE, echo=FALSE, results='asis'}
step02_01_01 <- function(){
  
    # 1. Definir rutas
    script_path <- str_R_script_file_path_internal
    RData_output_path <- str_RData_ENV_internal_file_path
    
    # 2. Crear un nuevo entorno vacío
    script_env <- new.env()
    
    # 3. Ejecución Silenciosa y Controlada
    cat(paste0("<b>Executing Internal Script:</b> <code>", fs::path_file(script_path), "</code><br>"))
    cat("<small style='color: #6c757d; font-style: italic;'>Action: Running isolated process and capturing environment.</small><br>")
    
    exec_result <- tryCatch({
      # Silenciamos cat(), print(), mensajes de carga y advertencias
      capture.output({
        suppressMessages(suppressWarnings({
          sys.source(script_path, envir = script_env)
        }))
      })
      TRUE # Retorno si todo sale bien
    }, error = function(e) {
      return(e$message) # Retorno del mensaje de error si falla
    })
    
    # 4. Verificación y Guardado
    if (isTRUE(exec_result)) {
      # Guardar solo si la ejecución fue exitosa
      save(list = ls(script_env), envir = script_env, file = RData_output_path)
      
      cat(paste0("<span style='color: #28a745;'>✔ <b>Success:</b> Environment exported to <code>", RData_output_path, "</code></span><br><br>"))
      
      # 5. Validación final del archivo físico
      the_output <- fn_check_single_file(str_file_path = RData_output_path)
      if(!the_output) knitr::knit_exit()
    
    } else {
      # Reporte de error estético
      cat("<span style='color: #dc3545;'>✘ <b>Runtime Error:</b> The script failed to complete.</span><br>")
      cat(paste0("<div style='background-color: #fff5f5; border-left: 3px solid #dc3545; padding: 8px; margin-top: 5px;'>",
                 "<small style='color: #b02a37;'><b>Technical Detail:</b> ", exec_result, "</small></div><br>"))
      knitr::knit_exit()
    }
    
  # the_output <- fn_delete_single_file(str_file_target = str_RData_ENV_internal_file_path)
  # if(!the_output) knitr::knit_exit()
}
step02_01_01()
```



# Export zzz_output files and folders.
```{r step_export, eval=TRUE, echo=FALSE, results='asis'}
the_output <- fn_export_files_zzz_output(str_path_from = str_folder_output_local, 
                                         str_path_to = str_folder_output_external,
                                         bln_overwrite = FALSE,
                                         bln_production = TRUE)
if(!the_output) knitr::knit_exit()
```



# Final Summary
```{r step_final_time_end, eval=TRUE, echo=FALSE, results='asis'}
# 1. Cálculos de tiempo
time_end <- Sys.time()
time_duration <- difftime(time_end, time_start, units = "auto")
str_duration <- format(time_duration, digits = 3)



# 3. Construcción del HTML (Asegurando que no haya espacios extraños al inicio)
html_summary <- paste0(
  "<hr>",
  "<div style='background-color: #f8f9fa; border: 1px solid #dee2e6; padding: 15px; border-radius: 5px; font-family: sans-serif; color: #333;'>",
  "  <b style='display: block; color: #495057; font-size: 1.1em; margin-bottom: 10px;'>🏁 Final Execution Summary</b>",
  "  <div style='margin-bottom: 5px;'>🕒 <b>Start Time:</b> ", format(time_start, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>🏁 <b>End Time:&nbsp;</b> ", format(time_end, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>⌛ <b>Total Duration:</b> <span style='color: #007bff; font-weight: bold;'>", str_duration, "</span></div>",
  "</div>",
  "<div style='text-align: center; margin-top: 10px;'><small style='color: #6c757d;'>End of Rscience Automated Runner</small></div>"
)

# Usamos cat con fill = TRUE para asegurar que el buffer se limpie correctamente
cat(html_summary, fill = TRUE)
```

