---
title: "Rscience"
format: 
  html: 
    output-file: "report01_lab03_RUN_RQuarto_HIDDEN_RUNNER.html"
    embed-resources: true
execute: 
  enabled: true
---

Tool: Rs003_LM_QQ_FIX_BAL_ANOVA_1Way_s001  
QMD File name: report01_lab03_RUN_RQuarto_HIDDEN_RUNNER.qmd


```{r step00_time_start, eval=TRUE, echo=FALSE, results='asis'}
# Captura del tiempo inicial
time_start <- Sys.time()

cat("<b>Runner Execution Started:</b>", format(time_start, "%Y-%m-%d %H:%M:%S"), "<br>")
cat("<hr>")
```

```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Libraries
library("fs")
library("knitr")
library("tidyverse")
library("kableExtra")

# Funtions
# source(file = "fn_local.R")
source(file = "fn_actions.R")
```

---

```{r basics, eval=TRUE, echo=FALSE, results='asis'}
# Files
   str_file_hidder_runner_html <- "report01_lab03_RUN_RQuarto_HIDDEN_RUNNER.html"

# Folders
   str_folder_input_external  <- "../lab01_RUN_create_files/zzz_output_local"
   str_folder_output_external <- "../../zzz_zzz_output"
   str_folder_output_local    <- "zzz_output_local"

   
```




# Copying all qmd files from external input folder
```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Folders
str_folder_FROM <- str_folder_input_external
str_folder_TO <- str_folder_output_local

vector_qmd_file_paths_FROM <- list.files(path = str_folder_FROM , 
                                            pattern = "\\.qmd$", 
                                            full.names = T)
vector_qmd_file_names <- basename(vector_qmd_file_paths_FROM)

vector_qmd_file_paths_TO <- file.path(str_folder_TO, vector_qmd_file_names)


```

# Copying files FROM-TO.
## FROM Folder: Folder external input must exists.
```{r step02_01_01, eval=TRUE, echo=FALSE, results='asis'}
step02_01_01 <- function(){
  
  the_output <- fn_check_single_folder(str_folder_target = str_folder_FROM)
  if(!the_output) knitr::knit_exit()
}
step02_01_01()
```

## FROM files: files must exists.
```{r step02_02_01, eval=TRUE, echo=FALSE, results='asis'}

step02_02_01 <- function(){
  



the_output <- fn_check_multi_files(vector_paths = vector_qmd_file_paths_FROM)
    if(!the_output) knitr::knit_exit()
}
step02_02_01()
```



## TO Folder: Folder local output must exists and be clean.
```{r step02_03_01, eval=TRUE, echo=FALSE, results='asis'}

step02_03_01 <- function(){
  
  the_output <- fn_check_single_folder(str_folder_target = str_folder_TO)
  if(!the_output) knitr::knit_exit()
}
step02_03_01()
```


```{r step02_03_02, eval=TRUE, echo=FALSE, results='asis'}
step02_03_02 <- function(){
  
  the_output <- fn_cleaning_single_folder(str_folder_target = str_folder_TO)
  if(!the_output) knitr::knit_exit()
}
step02_03_02()
```



## TO files: files must not exists.
```{r step02_04_01, eval=TRUE, echo=FALSE, results='asis'}

  
step02_04_01 <- function(){
  
  the_output <- fn_delete_multi_files(vector_paths = vector_qmd_file_paths_TO)
  if(!the_output) knitr::knit_exit()
}
step02_04_01()
```


## Copying files FROM-TO.
```{r step02_05_01, eval=TRUE, echo=FALSE, results='asis'}

step02_05_01 <- function(){
  
the_output <- fn_copy_verify_multi_files(vector_from = vector_qmd_file_paths_FROM, 
                           vector_to = vector_qmd_file_paths_TO)
if(!the_output) knitr::knit_exit()
}
step02_05_01()
```


## Verify existence after copy on TO.
```{r step02_05_02, eval=TRUE, echo=FALSE, results='asis'}

step02_05_02 <- function(){
  
the_output <- fn_check_multi_files(vector_paths = vector_qmd_file_paths_TO)
if(!the_output) knitr::knit_exit()
}
step02_05_02()
```


# Quarto - Render
## Pre render
```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}

library("quarto")

# Definimos la ruta de salida completa
str_qmd_input_file_name <- "report01_lab01_CopyMod_RQuarto_01_ANOVA.qmd"
str_html_output_file_name01 <- paste0(tools::file_path_sans_ext(str_qmd_input_file_name), ".html")
str_html_output_file_name02 <- "zzz_output_report01_lab03_RQuarto.html"

str_qmd_file_path <- file.path(str_folder_output_local, str_qmd_input_file_name)
str_old_file_path <- file.path(str_folder_output_local, str_html_output_file_name01)
str_new_file_path <- file.path(str_folder_output_local, str_html_output_file_name02)
```

```{r step03_01_01, eval=TRUE, echo=FALSE, results='asis'}

step03_01_01 <- function(){
  the_output <- fn_check_single_file(str_file_path = str_qmd_file_path)
  if(!the_output) knitr::knit_exit()
}
step03_01_01()
```

```{r step03_02_01, eval=TRUE, echo=FALSE, results='asis'}
step03_02_01 <- function(){
  
  the_output <- fn_delete_single_file(str_file_target = str_old_file_path)
  if(!the_output) knitr::knit_exit()
}
step03_02_01()
```

```{r step03_03_01, eval=TRUE, echo=FALSE, results='asis'}
step03_03_01 <- function(){
  
  the_output <- fn_delete_single_file(str_file_target = str_new_file_path)
  if(!the_output) knitr::knit_exit()
}
step03_03_01()
```

## Render
```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}

step03_04_01 <- function(){
  
quarto::quarto_render(
  input = str_qmd_file_path,
  execute_dir = str_folder_output_local,
  quiet = T
)

}
step03_04_01()
```


## Post Render
```{r step03_04_01, eval=TRUE, echo=FALSE, results='asis'}

step03_04_01 <- function(){
  the_output <- fn_check_single_file(str_file_path = str_old_file_path)
  if(!the_output) knitr::knit_exit()
}
step03_04_01()
```

```{r step03_04_02, eval=TRUE, echo=FALSE, results='asis'}

step03_04_02 <- function(){
the_output <- fn_rename_single_file(str_path_from = str_old_file_path, 
                      str_path_to = str_new_file_path)
if(!the_output) knitr::knit_exit()
}
step03_04_02()
```

```{r step03_05_01, eval=TRUE, echo=FALSE, results='asis'}

step03_05_01 <- function(){
  the_output <- fn_check_single_file(str_file_path = str_new_file_path)
  if(!the_output) knitr::knit_exit()
}
step03_05_01()
```


# Copy and past all "zzz_output" files to output user folder
```{r step07_01_01, eval=TRUE, echo=FALSE, results='asis'}



step07_01_01 <- function() {
  cat("<b>Step 07: Final Distribution</b><br>")
  
  # Listar archivos de forma robusta
# 1. Obtenemos TODOS los archivos de la carpeta local (sin carpetas)
  all_items <- fs::dir_ls(str_folder_output_local, type = "file")
  
  # 2. Filtramos el vector basándonos SOLO en el nombre del archivo (basename)
  # El patrón "zzz_output_" debe estar en el archivo, no en la carpeta.
  files_from <- all_items[grepl("zzz_output_", fs::path_file(all_items))]
  
  if (length(files_from) == 0) {
    cat("<span style='color: #dc3545;'>✘ <b>Error:</b> No output files found in local folder.</span><br>")
    return(FALSE)
  }
  
  # Construir rutas de destino de forma segura
  files_to <- fs::path(str_folder_output_external, fs::path_file(files_from))

  # Copiar y Verificar
  the_output <- fn_copy_verify_multi_files(vector_from = files_from, 
                                           vector_to   = files_to)
  
  if(!the_output) knitr::knit_exit()
  return(invisible(TRUE))
}
step07_01_01()
```


# Final Summary
```{r step_final_time_end, eval=TRUE, echo=FALSE, results='asis'}
# 1. Cálculos de tiempo
time_end <- Sys.time()
time_duration <- difftime(time_end, time_start, units = "auto")
str_duration <- format(time_duration, digits = 3)

# 2. Conteo de archivos
total_out <- length(list.files(str_folder_output_local, pattern = "^zzz_output_"))

# 3. Construcción del HTML (Asegurando que no haya espacios extraños al inicio)
html_summary <- paste0(
  "<hr>",
  "<div style='background-color: #f8f9fa; border: 1px solid #dee2e6; padding: 15px; border-radius: 5px; font-family: sans-serif; color: #333;'>",
  "  <b style='display: block; color: #495057; font-size: 1.1em; margin-bottom: 10px;'>🏁 Final Execution Summary</b>",
  "  <div style='margin-bottom: 5px;'>🕒 <b>Start Time:</b> ", format(time_start, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>🏁 <b>End Time:&nbsp;</b> ", format(time_end, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>⌛ <b>Total Duration:</b> <span style='color: #007bff; font-weight: bold;'>", str_duration, "</span></div>",
  "  <div style='margin-bottom: 5px;'>📦 <b>Generated Files:</b> ", total_out, " files in local output</div>",
  "</div>",
  "<div style='text-align: center; margin-top: 10px;'><small style='color: #6c757d;'>End of Rscience Automated Runner</small></div>"
)

# Usamos cat con fill = TRUE para asegurar que el buffer se limpie correctamente
cat(html_summary, fill = TRUE)
```
